\documentclass{article}

\title{External Evidence Manifest From Finite-Capacity Causal Networks}
\author{Abraham Greenman}
\date{}

\begin{document}
\maketitle

\section{Claim Boundary}

This Paper 10 scaffold records the EEM-001 upstream binding through the closed
Paper 9 conditional observed-catalog comparison observables theorem, the
EEM-002 finite external evidence record manifest rows, and the EEM-003 finite
reproduction protocol descriptor rows, and the EEM-004 Paper 9 comparison
compatibility rows, and the EEM-005 evidence stability/coarse-graining rows.
It also records EEM-006 Paper 9 regime consistency and the EEM-007 no-hidden
import audit. It does not prove external evidence manifest recovery, observed
particle catalog recovery, physical Standard Model content, physical particle
excitations, physical matter fields, physical gauge fields, physical quantum
dynamics, continuum quantum field theory, simulation-only promotion,
fit-only calibration, physical nature realization, or a unified field theory.

\section{Closed Evidence Rows}

EEM-002 defines finite external evidence record rows using only the recorded
Paper 9 finite comparison observable package, explicit finite
source/provenance metadata, finite tolerance metadata, finite reproduction and
review status flags, and the upstream finite-capacity theorem chain. EEM-002
does not import observed particle catalog recovery, physical Standard Model
content, physical particle excitations, continuum QFT, background Hilbert
bundles, simulation-only promotion, fit-only calibration, physical quantum
dynamics, physical nature promotion, or unified-field promotion.

\section{Active Obligation}

EEM-003 defines finite reproduction protocol descriptors without treating
simulation, fit, generated prose, external catalogs, or review status as
proof. EEM-004 proves compatibility with the closed Paper 9 observed-catalog
comparison descriptor, comparison-map, compatibility, and stability rows.
EEM-005 proves evidence stability and intrinsic coarse-graining stability.
EEM-006 binds the closed local Paper 10 structures to the recorded Paper 9
regime. EEM-007 closes the no-hidden import audit. EEM-008 is the next
substantive target: close the final conditional certificate.

\end{document}
